---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# otndata

<!-- badges: start -->
<!-- badges: end -->

`otndata` is a wrapper around the Ocean Tracking Network's Plone content management system setup.

## Installation

You can install the development version of otndata from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mhpob/otndata")
```

## Example

There are a few things that can be accessed without logging in. Mainly all of the information presented via the leaflet map that can be seen on <https://members.oceantrack.org>.

```{r example}
library(otndata)

otn_list_species() |>
  head()

otn_list_projects() |>
  head()

otn_list_stats()
```

You can also query projects according to code, country of origin, species, institution, node, or point of contact.

```{r}
otn_search_node("ACT") |>
  head()

otn_search_code("tail")

otn_search_contact("Mike O'Brien")
```


You'll likely need to log in to access other parts of the CMS. You can set your username and password for your system using the `otn_set_credentials` helper function.


```{r eval=FALSE}
otn_set_credentials()
```

After that, you can just log in using `otn_login`. This package is meant to interface with any node's Plone instance. You can switch between them using the `server` argument.

```{r login}
otn_login(server = 'devel')
```

List your project's files:

```{r}
otn_project_files(project = 'nsbs', server = 'devel', batch_size = 5)

otn_extract_files(project = 'nsbs', server = 'devel', batch_size = 5)
```

Or, just grab the ones modified more recently using the `since` argument:
```{r}
otn_project_files(
  project = 'nsbs',
  since = "2020-01-01",
  server = 'devel',
  batch_size = 5
)

otn_extract_files(
  project = 'nsbs',
  since = "2020-01-01",
  server = 'devel',
  batch_size = 5
)
```


You can download a file via its URL. This is a BIG work in progress and the API will likely change multiple times in the coming weeks.
```{r eval=FALSE}
otn_get_file(
  "https://members.devel.oceantrack.org/data/repository/nsbs/detection-extracts/nsbs_matched_detections_2017.zip"
)
```