---
title: "Access for ACT Network members"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Access for ACT Network members}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You've just received notifications that your ACT Network tag matches are in. Hooray!! Let's walk through how to interact with all of your data.

```{r setup}
library(otndata)
library(dplyr)
library(arrow)
```

First, we need to log in. If you have never entered your username and password before, you'll need to do so. Run the following:

```{r}
otn_login("act")
```

This will just set your credentials for the current R session. If you wish to use the same credentials after closing/reopening R, use `otn_set_credentials`:

```{r, eval=FALSE}
otn_set_credentials("act")
```

What you might first want to do is check out all of the data extract files on offer.

```{r}
otn_extract_files(project = "tailwinds")
```

This can be a lot! We can just grab the files that have been modified after a certain date -- usually the date just before the most-recent data push.


```{r}
otn_extract_files(project = "tailwinds", since = "2026-06-12")
```

The most important thing, however, is downloading those files! Let's grab the parquet files via `otn_extract_files`, download them with `otn_download`, and create a mini-database for ourselves.

```{r}
otn_extract_files(
  project = "tailwinds",
  since = "2026-06-12"
) |>
  dplyr::filter(grepl("_qualified.*parquet", name)) |>
  otn_download(outdir = "./my_awesome_detections")
```

Create a database on the fly using the [arrow package](https://arrow.apache.org/docs/r).

```{r}
my_db <- arrow::open_dataset("my_awesome_detections/")
my_db
```

Now we can do some really quick summaries.

```{r}
my_db |>
  dplyr::group_by(trackerCode) |>
  dplyr::tally() |>
  dplyr::arrange(-n) |>
  dplyr::collect()
```

Or find out who we should email and say "hi!".

```{r}
my_db |>
  dplyr::distinct(contactPI) |>
  dplyr::mutate(contactPI = sub(" \\(.*", "", contactPI)) |>
  head() |>
  dplyr::collect()
```


```{r, echo=FALSE, message=FALSE}
# Clean up the folder made above
rm(my_db)
gc(verbose = FALSE)
unlink("my_awesome_detections", recursive = T)
```